Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-24 analysis/paper/paper.Rmd
cite 'report' package
reknit manuscript and supplementary materials

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggridges",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "tidyr",
  "tools"
)

@@

A full report of all parameters and model details are available in the Supplementary Materials.
Additionally, all methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.

>>>>

```{r, setup, echo = FALSE, message=FALSE}
packages <- c(
  "DiagrammeR",
  "DiagrammeRsvg",
  "bayesplot",
  "bayestestR",
  "brms",
  "dplyr",
  "english",
  "extrafont",
  "flextable",
  "ggpubr",
  "here",
  "janitor",
  "knitr",
  "officer",
  "parameters",
  "patchwork",
  "posterior",
  "report",
  "rsvg",
  "tidyr",
  "tools"
)

@@

A full report of all parameters and model details are available in the Supplementary Materials generated using the contributed package 'report' (version `r packageVersion("report")`) [@Makowski2021].
Additionally, all methods are described in greater detail with the code necessary to reproduce the work in @Sparks2022.
